A Combinatorial Search of Parameterized Quantum Circuit Learning for Chemical Applications

### 2024-09-24 manuscript/main.tex
kill list + 5BSE
Clean up + New plan

@@

>>>>

\newpage
\textcolor{red}{Reorganize}
\begin{itemize}
	\item Abstract
	\item Introduction
	\item Methods
	\item Datasets
	\item Results
	\begin{itemize}
		\item Function fitting 
		\begin{itemize}
			\item Classical testing
			\item All (5 + 16 qubit)
			\item RUD + AL (5 + 16 qubit)
			\item Error mitigation
			\item Real device
		\end{itemize}
		\item BSE
		\begin{itemize}
			\item Classical testing
			\item All 5 qubit
			\item Truncated 16 qubit set (cost analysis 5 qubit)
			\item RUD + AL (5 + 16 qubit)
			\item Error mitigation
			\item Real device
		\end{itemize}		
		\item DDCC
		\begin{itemize}
			\item Classical testing
			\item Truncated  5 qubit set (based on BSE 5 qubit cost analysis)
			\item Truncated 16 qubit set (based on BSE 5 qubit cost analysis)
			\item RUD + AL (5 + 16 qubit)
			\item Error mitigation
			\item Real device
		\end{itemize}		
	\end{itemize}
	\item Discussion and Conclusion
\end{itemize}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=\linewidth]{images/AllBSE5_circuitdepth_MAE_vs_iterationtime.png}
	\caption{\textcolor{red}{ADD KILL LIST}}
	\label{fig:AllBSE5_circuitdepth_MAE_vs_iterationtime}
\end{figure}
